Exercise 2: Quality Attributes and Architectural Design of the HS07 System

### 2008-02-24 trunk/SAiP/Module1/H2/paper.tex
Adding 11 to the identical scenarios
Adding a little more about availability

\subsection{Selection}
Here we put the scenarios to the vote. This is done by emulation of a real-life situation where the actual stakeholder would
be part of the process. We take on the roles of the stakeholders in their absence, and chose which scenarios would be more
interesting for us.
\subsection{Stakeholders and interests}
\begin{itemize}
\item User (homeowner)
\begin{itemize}
\item Easy to use and configure
\item Always available
\item Safe (will not make an error and burn down the house)
\item Secure (other people cannot control my home)
\end{itemize}
\item Producer
\begin{itemize}
\item Cheap
\item Production line (modifiability for other uses)
\end{itemize}
\item Technical installer
\begin{itemize}
\item Easily deployable (installable)
\end{itemize}
\item Developer (?)
\begin{itemize}
\item Easily adjustable to new requirements
\item Scalable
\item Remote update (upgrading online)
\item Remote maintenance (debugging online)
\item Automatically testable (regression test)
\item Developing in parallel
\end{itemize}
\item Insurance company
\begin{itemize}
\item Safe with respect to fires (radiators) and break ins (door), ...
\end{itemize}
\end{itemize}
\subsection{Identical scenarios}
Due to the distributed location of the participants in the brainstorming multiple "similar" scenarios was created. In order to avoid having the same scenario represented twice with a slightly different wording, the below list show the scenarios which will be considered identical, meaning that their votes will be accumulated.
\begin{itemize}
\item 2. and 7.
\item 6. and 16.
\item 10. and 17.
\item 9. and 18.
\item 1. and 20.
\item 5. and 21.
\end{itemize}
\subsection{The Vote}
\subsection{First vote}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Person & Stakeholder Role & Vote 1 & Vote 2 & Vote 3 & Vote 4 & Vote 5 & Vote 6\\
\hline
Jesper&User&4&5&6/16&20&21&2/7\\
Lars&Developer&19&19&5/21&9/18&11&13\\
Anders&Producer&2/7&4&6/16&8&14&5/21\\
\hline
\end{tabular}
\subsection{Second vote}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Person & Stakeholder Role & Vote 1 & Vote 2 & Vote 3 & Vote 4 & Vote 5 & Vote 6\\
\hline
Jesper&Developer&11&19&9&11&13&6/16\\
Lars&User&1/20&4&6/16&15&4&5/21\\
Anders&Producer&9&6/16&11&12&17&9/18\\
\hline
\end{tabular}
\subsection{Voting Results}
This is the result of the vote in a prioritized order.
\begin{enumerate}
\item 9/18 (6 votes)
\item 11 (5 votes)
\item 5/21 (4 votes)
\item 6/16 (4 votes)
\item 19 (3 votes)
\item 4 (3 votes)
\item 13 (2 votes)
\item 1/20 (2 votes)
\item 2/7 (2 votes)
\item 10/17 (2 votes)
\item 12 (2 votes)
\item 15 (1 votes)
\item 3 (0 votes)
\item 8 (0 votes)
\item 14 (0 votes)
\end{enumerate}
\subsection{Refinement}
The process of refining the chosen scenarios centers around specification of various elements of the scenario. Stimulus, Response, Response Measurement.

@@

\subsection{Refined Scenario \#1}
\subsection{Tactics}
\subsection{Modifiablity}
\subsection{Testability}
\subsection{Refined Scenario \#3}
Scenario \#3 requires the HS07 system to provide a web interface that can be used to change the temperature in the house. The response requirements sets some requirements to the availability of the http service.
\subsection{Tactics}
\subsection{Availability}
As the user may experience non-responsiveness 0,1% of the time it is believed that this can be done with a single hardware unit (no HW-redundancy). At the same time the requirement of 30 seconds 1% of the time is sufficient time to restart the web-service, and it is believed sufficient to have \emph{passive redundancy}. Finally it is believed that an availability of 5 seconds 98,9% of the times, require a form of redundancy, \emph{passive redundancy} is chosen. As an example of a design may be mentioned the Apache web-server design, which is redundant processes. A number of processes is spawned to handle HTTP/GET requests, and it uses some kind of fault detection scheme to detect if one become non-responsive. If this happens it is simply killed and an identical process is spawned in its place.

>>>>

\subsection{Selection}
Here we put the scenarios to the vote. This is done by emulation of a real-life situation where the actual stakeholder would
be part of the process. We take on the roles of the stakeholders in their absence, and chose which scenarios would be more
interesting for us.
\subsection{Stakeholders and interests}
\begin{itemize}
\item User (homeowner)
\begin{itemize}
\item Easy to use and configure
\item Always available
\item Safe (will not make an error and burn down the house)
\item Secure (other people cannot control my home)
\end{itemize}
\item Producer
\begin{itemize}
\item Cheap
\item Production line (modifiability for other uses)
\end{itemize}
\item Technical installer
\begin{itemize}
\item Easily deployable (installable)
\end{itemize}
\item Developer (?)
\begin{itemize}
\item Easily adjustable to new requirements
\item Scalable
\item Remote update (upgrading online)
\item Remote maintenance (debugging online)
\item Automatically testable (regression test)
\item Developing in parallel
\end{itemize}
\item Insurance company
\begin{itemize}
\item Safe with respect to fires (radiators) and break ins (door), ...
\end{itemize}
\end{itemize}
\subsection{Identical scenarios}
Due to the distributed location of the participants in the brainstorming multiple "similar" scenarios was created. In order to avoid having the same scenario represented twice with a slightly different wording, the below list show the scenarios which will be considered identical, meaning that their votes will be accumulated.
\begin{itemize}
\item 2. and 7.
\item 6. and 16.
\item 10. and 17.
\item 9. and 11. and 18.
\item 1. and 20.
\item 5. and 21.
\end{itemize}
\subsection{The Vote}
\subsection{First vote}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Person & Stakeholder Role & Vote 1 & Vote 2 & Vote 3 & Vote 4 & Vote 5 & Vote 6\\
\hline
Jesper&User&4&5&6/16&20&21&2/7\\
Lars&Developer&19&19&5/21&9/18&11&13\\
Anders&Producer&2/7&4&6/16&8&14&5/21\\
\hline
\end{tabular}
\subsection{Second vote}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Person & Stakeholder Role & Vote 1 & Vote 2 & Vote 3 & Vote 4 & Vote 5 & Vote 6\\
\hline
Jesper&Developer&11&19&9&11&13&6/16\\
Lars&User&1/20&4&6/16&15&4&5/21\\
Anders&Producer&9&6/16&11&12&17&9/18\\
\hline
\end{tabular}
\subsection{Voting Results}
This is the result of the vote in a prioritized order.
\begin{enumerate}
\item 9/18 (6 votes)
\item 11 (5 votes)
\item 5/21 (4 votes)
\item 6/16 (4 votes)
\item 19 (3 votes)
\item 4 (3 votes)
\item 13 (2 votes)
\item 1/20 (2 votes)
\item 2/7 (2 votes)
\item 10/17 (2 votes)
\item 12 (2 votes)
\item 15 (1 votes)
\item 3 (0 votes)
\item 8 (0 votes)
\item 14 (0 votes)
\end{enumerate}
\subsection{Refinement}
The process of refining the chosen scenarios centers around specification of various elements of the scenario. Stimulus, Response, Response Measurement.

@@

\subsection{Refined Scenario \#1}
\subsection{Tactics}
\subsection{Modifiablity}
\subsection{Testability}
\subsection{Refined Scenario \#3}
Scenario \#3 requires the HS07 system to provide a web interface that can be used to change the temperature in the house. The response requirements sets some requirements to the availability of the http service.
\subsection{Tactics}
\subsection{Availability}
As the user may experience non-responsiveness 0,1% of the time it is believed that this can be done with a single hardware unit (no HW-reduadance, e.g. \emph{voting}). At the same time the requirement of 30 seconds 1% of the time is sufficient time to restart the web-service, and it is therefore not required to have \emph{active redundancy}. Finally it is believed that an availability of 5 seconds 98,9% of the times, require a form of redundancy, and for this reason \emph{passive redundancy} is chosen. As an example of a design may be mentioned the Apache web-server design, which is redundant processes. A number of processes is spawned to handle HTTP/GET requests, and it uses some kind of fault detection scheme to detect if one become non-responsive. If this happens it is simply killed and an identical process is spawned in its place.
